---
title: Pathogen Genomics Center of Excellence Situation Report
date: 4/26/2024
date-modified: today
bibliography: references.bib
---

```{r}
var <- "JN.1"
today_date <- Sys.Date()
```

```{=typst}
#import "@preview/showybox:2.0.1": showybox

// Second showybox
#showybox(
  title-style: (
    boxed-style: (
      anchor: (
        x: center,
        y: horizon
      ),
      radius: (top-left: 10pt, bottom-right: 10pt, rest: 0pt),
    )
  ),
  frame: (
    title-color: green.darken(40%),
    body-color: green.lighten(80%),
    footer-color: green.lighten(60%),
    border-color: green.darken(60%),
    radius: (top-left: 10pt, bottom-right: 10pt, rest: 0pt)
  ),
  title: "Key Findings",
  footer: text(size: 10pt, weight: 600, emph("Please see Situation Updates for COE group updates"))
)[
  
```
-   Current data reflects a mixture of `{r} var` descendents as the likely near term variants.\
-   Globally no other variants with unusual characteristics have been identified as having unusual growth.
-   Some other point

```{=typst}
    ]
```
# Situation Update Details

-   Based on what - XYZ(?), JN.1 and descendents continue to dominate. Some recombinations from JN.1 and other BA.5 variants are being monitoredtracked, but have yet to show significant growth relative other variants.
-   Together this diversity suggests steady evolution against general population immunity with no indications of a variant driven wave of COVID-19 infections.
-   As of `{r} today_date`, there were X samples from MM/DD/YYYY - MM/DD/YYYY, some comment on trend
-   Some text here about image one. There is this variant that's here
-   Some text about image two
-   Image 3 has this
-   Findings from a site's analysis of national data

{{< embed notebooks/nwcoe.qmd#fig-countprop >}}

```{r}
#| eval: true
#| echo: false
#| warning: false
#| message: false

# Here you can write code that can be used as inline text
# See the variant proportions values below in the summary
# Those values are not hard-coded/written. They will be automatically updated 
# in the text whenever there is new data/a new render

wa_prop <- paste0(50,"%")
ga_prop <- 60
ne_prop <- 50
va_prop <- paste0(60,"%")

```


```{=typst}
#showybox(
  title: "Site Summaries"
)[


```

:::{.content-visible when-format="html"}
# Site Summaries
:::

-   Washington State Department of Health - highest variant proportion is `{r} wa_prop`
-   Georgia Department of Public Health probablity of detection: `{r} ga_prop` and the consensus genomes are uploaded to public repositories like GISAID and GenBank.
-   Massachusetts Department of Health prop - `{r} ne_prop`
-   Virginia Deparment of Health - `{r} va_prop`

```{=typst}

  ]
```


{{< embed notebooks/necoe.qmd#fig-state-analysis >}}

{{< embed notebooks/vacoe.qmd#fig-fatality-plot >}}

## Citations

This is a simple placeholder for the manuscript's main document [@knuth84].

[@fig-countprop code source](https://coe-test-org.github.io/sitrep-demo/notebooks/nwcoe-preview.html#cell-fig-countprop)

[@fig-state-analysis code source](https://coe-test-org.github.io/sitrep-demo/notebooks/necoe-preview.html#cell-fig-state-analysis)

[@fig-fatality-plot code source](https://coe-test-org.github.io/sitrep-demo/notebooks/vacoe-preview.html#cell-fig-fatality-plot)

[main article code source](https://coe-test-org.github.io/sitrep-demo/index-preview.html)
